---
title: "StatAna"
author: "Group4"
date: "8/10/2021"
output: html_document
---
This script includes the preprocessing and analyses preregistered for our replication of the study by Westera & Brasoveanu "Ignorance in context: The interaction of modified numerals and QUDs" (2014).

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r libraries, include = FALSE}
library(tidyverse)
library(brms)
library(tidyboot)
library(tibble)
library(dplyr)
library(data.table)
library(ggplot2)

library(ordinal)
library(lme4)
library(lmerTest)
library(lmtest)
```


```{r data, include=FALSE}
# read in data
data <- read_csv("~/Documents/Uni/Semester6/XPLab/results_277_Group4_pilot_Group4.csv")
glimpse(data)
```

``` {r counts}
# some initial counts of the trial kinds for checking
data %>% count(type)
data %>% group_by(submission_id) %>% count(type)
```
```{r splits}
# get filler trials 
data_filler <- data %>% filter(type == "filler-implau" |type == "filler-plau" | type =="filler-oi" | type =="filler-ov")
glimpse(data_filler)
# get main trials
data_main <- data %>% filter(type == "main")
glimpse(data_main)
```
## Exclusion
Create exclusion criteria: Exclude participants with answer on implausble filler with 4/5 more than 3 times
``` {r exclusion rules}
# create list of to exclude participants based on amounts of unfitting filler answers
# changed to 5 for pilot study to use all data sets
to_exclude_sub_ids <- data_filler %>% group_by(submission_id) %>% filter(type == "filler-implau" & (response == "4" | response == "5")) %>% filter(length(submission_id) > 10) %>%  distinct(submission_id)
glimpse(to_exclude_sub_ids)
```
Apply exclusion criteria to create cleaned data set with main trials
``` {r exclusion}
if (nrow(to_exclude_sub_ids) > 0){
  data_cleaned <- data %>% filter(submission_id != to_exclude_sub_ids[['submission_id']]) %>% filter(type == "main") } else {
    data_cleaned <- data
  }
```

``` {r data splitting}
# select relevant columns, only main trials are used here!
data_wrang <- data_cleaned %>% select(submission_id, condition, response, id, trial_name, trial_number) 

data_quest <- data_wrang %>% filter(trial_name == "question_view")
data_quest %>% pivot_wider(
  names_from = condition,
  values_from = response
) %>% select(submission_id, id, trial_number, HOWMANY, WHAT, POLAR)

data_answ <- data_wrang %>% filter(trial_name == "answer_view")
data_answ %>% pivot_wider(
  names_from = condition,
  values_from = response
) %>% select(submission_id, id, trial_number, SUP, COMP)

data_conc <- data_wrang %>% filter(trial_name == "conclusion_view")
data_conc %>% pivot_wider(
  names_from = trial_name,
  values_from = response
) %>% rename(score = conclusion_view) %>% select(submission_id, id, trial_number, score)

#combining tibble
first <- full_join(data_quest, data_answ, by = "trial_number")
second <- full_join(first, data_conc, by = "trial_number")
sel <- second %>% select(submission_id, trial_number, condition.x, condition.y, response, id)
sel$combi <- with(sel,factor(paste(condition.x,condition.y)))
#second %>% as.numeric(unlist(second[['response']]))
sel$response <- as.numeric(sel$response) 
as_tibble(sel)
fig <- aggregate(sel[, 5], list(sel$condition.x, sel$condition.y), mean)
#fig <- fig %>% mutate(sd = aggregate(sel[, 5], list(sel$condition.x, sel$condition.y), sd))
as_tibble(fig)
```


``` {r init plot}
ggplot(fig, aes(x = Group.1, y = response, colour = Group.2)) + geom_point()
```

``` {r factors}
# random effects: submission_id (=participant), id (=item)
# data stored in sel
# dependent variable: response
# independent variable/fixed effects: condition.x, condition.y
# (1|id) : 1 = intercept --> each id is allowed ot have its own intercept

# factorise data
mod <- sel
mod$response <- factor(sel$response)
mod$condition.x <- factor(sel$condition.x)
mod$condition.y <- factor(sel$condition.y)

levels(mod$condition.x)
```
## Models
### Entire dataset
``` {r model 1}
# main effect
# entire dataset
fm1 <- clmm(
  formula = response ~ condition.x + condition.y + (1|submission_id) + (1|id),
  data = mod
)
summary(fm1)
```
``` {r model 2}
# interaction effects :
# entire data set
fm2 <- clmm(
  formula = response ~ condition.x * condition.y + (1|submission_id) + (1|id),
  data = mod
)
summary(fm2)
```

### Subsets by QUD type
Main Effects
``` {r model 3}
# main effect
# subset POLAR
fm3 <- clmm(
  formula = response ~ condition.x + condition.y + (1|submission_id) + (1|id),
  data = mod,
  subset = levels(condition.x == "POLAR")
)
summary(fm3)
```

``` {r model 4}
# main effect
# subset WHAT
fm4 <- clmm(
  formula = response ~ condition.x + condition.y + (1|submission_id) + (1|id),
  data = mod,
  subset = levels(condition.x == "WHAT")
)
summary(fm4)
```

``` {r model 5}
# main effect
# subset HOWMANY
fm5 <- clmm(
  formula = response ~ condition.x + condition.y + (1|submission_id) + (1|id),
  data = mod,
  subset = levels(condition.x == "HOWMANY")
)
summary(fm5)
```

Interaction Effects
``` {r model 6}
# interaction effect
# subset POLAR
fm6 <- clmm(
  formula = response ~ condition.x * condition.y + (1|submission_id) + (1|id),
  data = mod,
  subset = levels(condition.x == "POLAR")
)
summary(fm6)
```

``` {r model 7}
# interaction effect
# subset WHAT
fm7 <- clmm(
  formula = response ~ condition.x * condition.y + (1|submission_id) + (1|id),
  data = mod,
  subset = levels(condition.x == "WHAT")
)
summary(fm7)
```

``` {r model 8}
# interaction effects
# subset HOWMANY
fm8 <- clmm(
  formula = response ~ condition.x * condition.y + (1|submission_id) + (1|id),
  data = mod,
  subset = levels(condition.y == "HOWMANY")
)
summary(fm8)
```

# LR test
```{r LR test}
# interaction vs main effect: entire dataset
main <- fm1
inter <- fm2

lrtest(main, inter)
```


